Abb Analysis

### 2017-03-06 abbDataAnalysis_Script.Rmd
adding offline option
outputing data from pref analysis

  rawocc.pplot <- abbPrefPlot(str.data.ic,
                               x.field='occ.rate',
                               split.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.35 ,
                              spl.col=sm.col)
  rawocc.pplot

@@

  qtlocc.pplot <- abbPrefPlot(str.data.ic,
                               x.field='occ.qtl',
                               split.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.75)
  qtlocc.pplot <- qtlocc.pplot +
    xlab('\nQualtile of Occupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='nightly.rate',
                pref.field='str.ext.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='nightly.rate',
                            pref.field='str.ext.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm

>>>>

  rawocc.pplot <- abbPrefPlot(str.data.ic,
                               x.field='occ.rate',
                               split.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.35 ,
                              spl.col=sm.col)
  rawocc.pplot$plot

@@

  qtlocc.pplot <- abbPrefPlot(str.data.ic,
                               x.field='occ.qtl',
                               split.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.75)
  qtlocc.pplot <- qtlocc.pplot$plot +
    xlab('\nQualtile of Occupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.ext.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.ext.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm
